Supplementary Appendix: Trends in age-standardized mortality rates for blacks and whites by cause and sex, 1969-2013, United States

### 2017-05-19 Manuscript/Appendix-agestd-mort-rates.Rmd
modified supp app

mortality.rates <- reorder.as.map(mortality.rates, "state", "stabbrs")
mortality.rates.diff <- reorder.as.map(mortality.rates.diff, "state", "stabbrs")
```

@@

    c$x$data[[i]]$text <- gsub("rate.per.100k_mean", "Mean mortality rate", c$x$data[[i]]$text)
    c$x$data[[i]]$text <- gsub("rate.per.100k_lcl", "Lower credible limit", c$x$data[[i]]$text)
    c$x$data[[i]]$text <- gsub("rate.per.100k_ucl", "Upper credible limit", c$x$data[[i]]$text)
  }

@@

    d$x$data[[i]]$text <- gsub("rate.difference_mean", "Mean excess mortality", d$x$data[[i]]$text)
    d$x$data[[i]]$text <- gsub("rate.difference_LCL", "Lower credible limit", d$x$data[[i]]$text)
    d$x$data[[i]]$text <- gsub("rate.difference_UCL", "Upper credible limit", d$x$data[[i]]$text)
  }

@@

**eFigure 1: Age-standardized trends in CVD-related mortality in black and white men, United States, 1969-2013**

```{r print-em, fig.width = 9, fig.height = 9, echo = F}
Cardiovascular.Male.mort.plot[[3]] %>% layout(margin = list(b = 100))
Cardiovascular.Male.mort.plot[[4]]
```

**eFigure 2: Age-standardized trends in CVD-related mortality in black and white women, United States, 1969-2013**

```{r print-em-2, fig.width = 9, fig.height = 9, echo = F}
Cardiovascular.Female.mort.plot[[3]] %>% layout(margin = list(b = 100))
Cardiovascular.Female.mort.plot[[4]]
```

**eFigure 3: Age-standardized trends in cancer-related mortality in black and white men, United States, 1969-2013**

```{r print-em-3, fig.width = 9, fig.height = 9, echo = F}
Cancers.Male.mort.plot[[3]] %>% layout(margin = list(b = 100))
Cancers.Male.mort.plot[[4]]
```

**eFigure 4: Age-standardized trends in cancer-related mortality in black and white women, United States, 1969-2013**

```{r print-em-4, fig.width = 9, fig.height = 9, echo = F}
Cancers.Female.mort.plot[[3]] %>% layout(margin = list(b = 100))
Cancers.Female.mort.plot[[4]]
```

**eFigure 5: Age-standardized trends in mortality related to non-communicable disease in black and white men, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 9, echo = F}
`Non-communicable.Male.mort.plot`[[3]] %>% layout(margin = list(b = 100))
`Non-communicable.Male.mort.plot`[[4]]
```

**eFigure 6: Age-standardized trends in mortality related to non-communicable disease in black and white women, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 9, echo = F}
`Non-communicable.Female.mort.plot`[[3]] %>% layout(margin = list(b = 100))
`Non-communicable.Male.mort.plot`[[4]]
```

**eFigure 7: Age-standardized trends in injury-related mortality in black and white men, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 9, echo = F}
Injuries.Male.mort.plot[[3]] %>% layout(margin = list(b = 100))
Injuries.Male.mort.plot[[4]]
```

**eFigure 8: Age-standardized trends in injury-related mortality in black and white women, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 9, echo = F}
Injuries.Female.mort.plot[[3]] %>% layout(margin = list(b = 100)) 
Injuries.Female.mort.plot[[4]]
```

**eFigure 9: Age-standardized trends in mortality related to communicable disease in black and white men, United States, 1969-2013**

```{r print-3, fig.width = 9, fig.height=9, echo = F}
Communicable.Male.mort.plot[[3]] %>% layout(margin = list(b = 100))
Communicable.Male.mort.plot[[4]]
```

**eFigure 10: Age-standardized trends in mortality related to communicable disease in black and white women, United States, 1969-2013**

```{r print-4, fig.width = 9, fig.height=9, echo = F}
Communicable.Female.mort.plot[[3]] %>% layout(margin = list(b = 100))
Communicable.Female.mort.plot[[4]]
```

**eFigure 11: Age-standardized trends in mortality from all other causes in black and white men, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 9, echo = F}
`All other causes.Male.mort.plot`[[3]] %>% layout(margin = list(b = 100))
`All other causes.Male.mort.plot`[[4]]
```

**eFigure 12: Age-standardized trends in mortality from all other causes in black and white women, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 9, echo = F}
`All other causes.Female.mort.plot`[[3]] %>% layout(margin = list(b = 100)) 
`All other causes.Female.mort.plot`[[4]]
```

>>>>

mortality.rates <- reorder.as.map2(mortality.rates, "state", "stabbrs")
mortality.rates.diff <- reorder.as.map2(mortality.rates.diff, "state", "stabbrs")
```

@@

    c$x$data[[i]]$line$width <- 1 #make all the lines thin
    c$x$data[[i]]$text <- gsub("rate.per.100k_mean", "Mean mortality rate", c$x$data[[i]]$text)
    c$x$data[[i]]$text <- gsub("rate.per.100k_lcl", "Lower credible limit", c$x$data[[i]]$text)
    c$x$data[[i]]$text <- gsub("rate.per.100k_ucl", "Upper credible limit", c$x$data[[i]]$text)
  }

@@

    d$x$data[[i]]$line$width <- 1 #make all the lines thin
    d$x$data[[i]]$text <- gsub("rate.difference_mean", "Mean excess mortality", d$x$data[[i]]$text)
    d$x$data[[i]]$text <- gsub("rate.difference_LCL", "Lower credible limit", d$x$data[[i]]$text)
    d$x$data[[i]]$text <- gsub("rate.difference_UCL", "Upper credible limit", d$x$data[[i]]$text)
  }

@@

**Figure S1: Age-standardized trends in CVD-related mortality in black and white men, United States, 1969-2013**

```{r print-em, fig.width = 9, fig.height = 7, echo = F}
Cardiovascular.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cardiovascular.Male.mort.plot[[4]]
```

**Figure S2: Age-standardized trends in CVD-related mortality in black and white women, United States, 1969-2013**

```{r print-em-2, fig.width = 9, fig.height = 7, echo = F}
Cardiovascular.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cardiovascular.Female.mort.plot[[4]]
```

**Figure S3: Age-standardized trends in cancer-related mortality in black and white men, United States, 1969-2013**

```{r print-em-3, fig.width = 9, fig.height = 7, echo = F}
Cancers.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cancers.Male.mort.plot[[4]]
```

**Figure S4: Age-standardized trends in cancer-related mortality in black and white women, United States, 1969-2013**

```{r print-em-4, fig.width = 9, fig.height = 7, echo = F}
Cancers.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cancers.Female.mort.plot[[4]]
```

**Figure S5: Age-standardized trends in mortality related to non-communicable disease in black and white men, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 7, echo = F}
`Non-communicable.Male.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`Non-communicable.Male.mort.plot`[[4]]
```

**Figure S6: Age-standardized trends in mortality related to non-communicable disease in black and white women, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 7, echo = F}
`Non-communicable.Female.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`Non-communicable.Male.mort.plot`[[4]]
```

**Figure S7: Age-standardized trends in injury-related mortality in black and white men, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 7, echo = F}
Injuries.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Injuries.Male.mort.plot[[4]]
```

**Figure S8: Age-standardized trends in injury-related mortality in black and white women, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 7, echo = F}
Injuries.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70)) 
#Injuries.Female.mort.plot[[4]]
```

**Figure S9: Age-standardized trends in mortality related to communicable disease in black and white men, United States, 1969-2013**

```{r print-3, fig.width = 9, fig.height = 7, echo = F}
Communicable.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Communicable.Male.mort.plot[[4]]
```

**Figure S10: Age-standardized trends in mortality related to communicable disease in black and white women, United States, 1969-2013**

```{r print-4, fig.width = 9, fig.height = 7, echo = F}
Communicable.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Communicable.Female.mort.plot[[4]]
```

**Figure S11: Age-standardized trends in mortality from all other causes in black and white men, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 7, echo = F}
`All other causes.Male.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`All other causes.Male.mort.plot`[[4]]
```

**Figure S12: Age-standardized trends in mortality from all other causes in black and white women, United States, 1969-2013**

```{r, fig.width = 9, fig.height = 7, echo = F}
`All other causes.Female.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70)) 
#`All other causes.Female.mort.plot`[[4]]
```
